Lasso_RCI_Response

### 2024-05-11 Lasso_RCI_Response.Rmd
ACT Scores???

# Libraries
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
```

@@

## Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
#DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
dim(Mothership)
```

@@

Mothership_lasso <- Mothership_post |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  #!is.na(Anxiety_Responder),
  ) |>
  select( c(
    ID1,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post,
  ))
Mothership_lasso_1 <- na.omit(Mothership_lasso)
dim(Mothership_lasso_1)

@@

# Data analysis 
## Part 1: Methods information
```{r}

@@

### Final relaxed lasso- Depression
Minimum- 
```{r}
## install.packages("fuzzySim")
library(fuzzySim) ## For FDR adjusted p values
library(broom) # for tidy regression output

@@

  # glm_min_dep <-
  #           glm(
  #     #Outcome varaible
  #       Depression_Responder ~
  #     # predictors
  #       Age_1  +
  #       Days_complete_1 + Days_not_attended_1 + Anxiety_D + 
  #       BPD_Co_C + Current_Dx + CUXOS_pre+
  #       rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
  #     #data
  #       data = Vars_dep,
  #     # type of regression : logistic = binary / binomial
  #       family = "binomial",
  #     )

install.packages("rempsyc")
library(rempsyc)
nice_table(tidy.summary.min.dep)

@@

## min model
  glm_min_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Age_1 + Married + Days_complete_1 + Days_not_attended_1 + Anxiety_D + 
        Substance_C + Trauma_D + Other + Mood_C + BPD_Co_C + Substance_C + 
        CUXOS_pre + 
        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")

@@

# Odds ratio
  OR.min.anx <- round(exp(coef(glm_min_anx)),3)
# OR 95% CI
  CI.min.anx <- data.frame(exp(confint(glm_min_anx)))
  CI.min.anx[,1] = round(CI.min.anx[,1],3)
  CI.min.anx[,2] = round(CI.min.anx[,2],3)
# P values
  p.values.min.anx <- data.frame(cbind(tidy.summary.min.anx$term,tidy.summary.min.anx$p.value))
  # FDR Adjusted P Values
    adj.p.min.anx <- FDR(pvalues = p.values.min.anx)
    ADJ.p.values.min.anx <- data.frame(rbind(adj.p.min.anx$exclude, adj.p.min.anx$select))
    ADJ.p.values.min.anx
# R^2 values  
   R2.min.anx <- performance::r2(glm_min_anx)
   R2.min.anx
# df for Forrest plots
FP.min.anx <- data.frame(cbind(
  Variable = tidy.summary.min.anx$term[2:length(tidy.summary.min.anx$term)],
  OR = OR.min.anx [2:length(OR.min.anx)],
  OR_low  = CI.min.anx [2:length(CI.min.anx$X2.5..),1],
  OR_high = CI.min.anx [2:length(CI.min.anx$X97.5..),2],
  p.values = p.values.min.anx$X2[2:length(p.values.min.anx$X2)]
                    ))

@@

#Change the names of variables
FP_anx$Variable = c("Age", "Unmarried", "Days Completed", 
                    "Days Not Attended", "Anixety Disorder","Co-SUD", 
                    "Trauma Disorder", "Other Disorder", "Co-Mood Disorder", 
                    "Co-BPD", "CUXOS Pre", "Post Coping", 
                    "Post PMH", "Post Functioning", "Post Wellbeing")

@@

FP_dep_m <- FP_dep |>
  ggplot(aes(y = reorder(Variable, -order), color = as.factor(sig))) +
  #take away background
  theme_classic() +
  #make the forrest plot
  geom_point(aes(x=OR), shape= FP_dep$sig,
               # ifelse(FP_dep$p.adjusted <= 0.05, 
               #                        16, # colored ones for significant varaibles
               #                        1), # uncolored ones for insignificant varaibles
             size=4,show.legend = FALSE) +
  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.35, show.legend = FALSE)+
  scale_color_manual(values = c("darkgrey","blue"))+
  #change x axis name
  labs(
    x="Odds Ratio") +
    # title = "Odds of Anxiety Treatment Non-Response",
    # subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
  #adjust the dimentions. 
  coord_cartesian(ylim = c(1,length(FP_dep$Variable) + 1)) +
  #add a line at 1 for reference 
   geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
  #add anotations to help suggests what each side means.
  annotate("text", x = .75, y = length(FP_dep$Variable) + 1, label = "Less Likely", size= 4) +
  annotate("text", x = 1.25, y = length(FP_dep$Variable) + 1, label = "More Likely",size= 4) +
  #Git rid of the Y - Axis
    theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        axis.text.y= element_blank(),
        axis.title.y= element_blank())

>>>>

# Libraries
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
library(fuzzySim) ## For FDR adjusted p values
library(broom) # for tidy regression output
```

@@

## Read in the dataset. 
```{r}
Mothership1 <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
#DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
Mothership1

list.files("~/Desktop/Coding/data/ACT_scores")
# path = "~/Desktop/Coding/data/ACT_scores"
# # 
# length(dir(path))
# for(i in dir(path))
# {
#   df_1 <- read_sav(paste0(path,"/",i))
#   Mothership_mindful <- left_join(Mothership1,df_1, by = join_by(ID1 == ID1))
# }

df_1 <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPost_1.sav")
Mothership1 <- left_join(Mothership1,df_1, by = join_by(ID1 == ID1))
df_2 <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPre_1.sav")
Mothership1 <- left_join(Mothership1,df_2, by = join_by(ID1 == ID1))
df_3 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_1.sav")
Mothership1 <- left_join(Mothership1,df_3, by = join_by(ID1 == ID1))
df_4 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_4250-4350.sav")
Mothership1 <- left_join(Mothership1,df_4, by = join_by(ID1 == ID1))
df_5 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPre_1.sav")
Mothership1 <- left_join(Mothership1,df_5, by = join_by(ID1 == ID1))

view(Mothership_mindful)
```

@@

Mothership_lasso <- Mothership_post |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  #!is.na(Anxiety_Responder),
  ) |>
  select( c(
    ID1,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post,
  ))
Mothership_lasso_1 <- na.omit(Mothership_lasso)

@@

# Data analysis 
## Part 1: Methods information
```{r}
summary(as.factor(Mothership_post_joined$SCID_1))
```

@@

### Final relaxed lasso- Depression
Minimum- 
```{r}
## install.packages("fuzzySim")

@@

# install.packages("rempsyc")
# library(rempsyc)
# nice_table(tidy.summary.min.dep)

@@

## min model
  glm_min_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Age_1 + Married + Days_complete_1 + 
        Days_not_attended_1 + Anxiety_D + Trauma_D +
        Other + Mood_C + BPD_Co_C + 
        Substance_C + CUXOS_pre +  rdqPOST_coping + 
        rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")

@@

# Odds ratio
  OR.min.anx <- round(exp(coef(glm_min_anx)),3)
# OR 95% CI
  CI.min.anx <- data.frame(exp(confint(glm_min_anx)))
  CI.min.anx[,1] = round(CI.min.anx[,1],3)
  CI.min.anx[,2] = round(CI.min.anx[,2],3)
# P values
  p.values.min.anx <- data.frame(cbind(tidy.summary.min.anx$term,tidy.summary.min.anx$p.value))
  # FDR Adjusted P Values
    adj.p.min.anx <- FDR(pvalues = p.values.min.anx)
    ADJ.p.values.min.anx <- data.frame(rbind(adj.p.min.anx$exclude, adj.p.min.anx$select))
    ADJ.p.values.min.anx
# R^2 values  
   R2.min.anx <- performance::r2(glm_min_anx)
   R2.min.anx

#wald
   library(aod)
   wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms= 2:15)

# df for Forrest plots
FP.min.anx <- data.frame(cbind(
  Variable = tidy.summary.min.anx$term[2:length(tidy.summary.min.anx$term)],
  OR = OR.min.anx [2:length(OR.min.anx)],
  OR_low  = CI.min.anx [2:length(CI.min.anx$X2.5..),1],
  OR_high = CI.min.anx [2:length(CI.min.anx$X97.5..),2],
  p.values = p.values.min.anx$X2[2:length(p.values.min.anx$X2)]
                    ))

@@

#Change the names of variables
FP_anx$Variable = c("Age", "Unmarried", "Days Completed", 
                    "Days Not Attended", "Anixety Disorder","Trauma Disorder", 
                    "Other Disorder", "Co-Mood Disorder",  "Co-BPD", 
                    "Co-SUD", "CUXOS Pre", "Post Coping", 
                    "Post PMH", "Post Functioning", "Post Wellbeing")

@@

FP_dep_m <- FP_dep |>
  ggplot(aes(y = reorder(Variable, -order), color = as.factor(sig))) +
  #take away background
  theme_classic() +
  #make the forrest plot
  geom_point(aes(x=OR), shape= FP_dep$sig,
               # ifelse(FP_dep$p.adjusted <= 0.05, 
               #                        16, # colored ones for significant varaibles
               #                        1), # uncolored ones for insignificant varaibles
             size=4,show.legend = FALSE) +
  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.35, show.legend = FALSE)+
  scale_color_manual(values = c("darkgrey","blue"))+
  #change x axis name
  labs(
    x="Odds Ratio") +
    # title = "Odds of Anxiety Treatment Non-Response",
    # subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
  #adjust the dimentions. 
  coord_cartesian(ylim = c(1,length(FP_dep$Variable) + 1),
                  xlim = c(.5,1.5)) +
  #add a line at 1 for reference 
   geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
  #add anotations to help suggests what each side means.
  annotate("text", x = .75, y = length(FP_dep$Variable) + 1, label = "Less Likely", size= 4) +
  annotate("text", x = 1.25, y = length(FP_dep$Variable) + 1, label = "More Likely",size= 4) +
  #Git rid of the Y - Axis
    theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        axis.text.y= element_blank(),
        axis.title.y= element_blank())
